Plots for Latent Hawkes Paper

### 2020-12-04 output_scripts/Paper_Plots.Rmd
tidy up and adjust plots as needed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

@@

```{r fig-3b-rank-comparison}
# current_cohort <- 5

@@

<!-- # Redone Figure 3 -->

<!-- As discussed, it would be interesting to redo figure 3b -->
<!-- to show the lack of fit in model 2 for one specific pair. This can be somewhat -->
<!-- extracted from the diagnostics file. -->

<!-- We actually want the empirical CDF plot here. -->

<!-- ```{r fig_3b_update, fig.height=7, include=FALSE, eval=FALSE} -->
<!-- # 2 -> 11 might be good here -->
<!-- # current_cohort <- 5 -->
<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
<!--   dplyr::summarize(count=n(), -->
<!--             observe=list(observe.id), -->
<!--             observe.length=list(observe.time), -->
<!--             no.events=list(no.events))  -->
<!-- top_pairs <- unique_pairs_df %>% arrange(desc(count)) -->

<!-- best_i <- top_pairs$initiator[8] -->
<!-- best_j <- top_pairs$recipient[8] -->

<!-- current_i <- best_i #8 -->
<!-- current_j <- best_j #2 -->

<!-- ### then plots #### -->
<!-- # par(mfrow = c(1, 2), oma = c(1, 1, 1, 1), -->
<!-- #      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0)) -->
<!-- # layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3)) -->
<!-- anno.cex <- 1.3 -->
<!-- title.cex <- 2.2 -->
<!-- title.line <- 0.5 -->
<!-- y.upper <- 20 -->
<!-- #### then the corresponding QQ plot #### -->
<!-- load(paste(data_path,cohort_names[current_cohort], -->
<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!-- Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]] -->

<!-- p <- ppoints(length(Lambda.dc_hawkes.test)) -->
<!-- # 100 equally spaced points on (0,1), excluding endpoints -->
<!-- q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) -->
<!-- # percentiles of the sample distribution -->
<!-- plot(qexp(p),q, -->
<!--      xlab="",ylab="",xaxt="n",yaxt="n", -->
<!--      pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5)) -->
<!-- mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex) -->
<!-- mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex) -->
<!-- mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2) -->
<!-- # Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1) -->
<!-- # Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1) -->
<!-- qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5) -->

<!-- ### Empirical CDF #### -->

<!-- plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE, -->
<!--      verticals = TRUE, col = viridis::viridis(1), lwd = 2,  -->
<!--      xlab = "", ylab = "", xaxt = "n", yaxt = "n", -->
<!--      main = "", col.01line = NULL) -->
<!-- curve(pexp(x,1/mean(Lambda.dc_hawkes.test)), -->
<!--       min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test), -->
<!--       ylab = "", xlab = "", -->
<!--       add = TRUE, lwd = 2) -->

<!-- ``` -->

<!-- ```{r repeat entire fig2b for model 2, include=extra_plots, eval=extra_plots} -->
<!-- # current_cohort <- 5 -->

<!-- load(paste(data_path,cohort_names[current_cohort], -->
<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->

<!-- load(paste(data_path,cohort_names[current_cohort], -->
<!--            "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
<!--            ".RData",sep='')) -->
<!-- eta1_mean <- mean(sim_cohort_dchp$eta_1) -->
<!-- eta2_mean <- mean(sim_cohort_dchp$eta_2) -->
<!-- eta3_mean <- mean(sim_cohort_dchp$eta_3) -->
<!-- f_est <- apply(sim_cohort_dchp$f,2,mean) -->
<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
<!--   dplyr::summarize(count=n(), -->
<!--                    observe=list(observe.id), -->
<!--                    observe.length=list(observe.time), -->
<!--                    no.events=list(no.events)) -->
<!-- unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->

<!-- ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
<!-- n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
<!-- Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number) -->
<!-- for(k in 1:mice_number){ -->
<!--   for(l in c(1:mice_number)[-k]){ -->
<!--     i<-expert_rank_10[[current_cohort]][k] -->
<!--     j<-expert_rank_10[[current_cohort]][l] -->
<!--     pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--     if(length(pair)>0){ -->
<!--       param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]), -->
<!--                          alpha=model1_fn$alpha.fun(f_est[i], -->
<!--                                                    f_est[j], -->
<!--                                                    eta1_mean, -->
<!--                                                    eta2_mean, -->
<!--                                                    eta3_mean), -->
<!--                          beta=mean(sim_cohort_dchp$beta)) -->
<!--       current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--       all_Lambda <- numeric(0) -->
<!--       for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
<!--         cur_win <- current_window_vec[cur] -->
<!--         current_event_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient == j & -->
<!--                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--         current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                         return_df$recipient==j& -->
<!--                             return_df$observe.id==cur_win,"observe.time"] -->
<!--         Lambda_vec <- uniHawkesCompensator(object = param_mean, -->
<!--                               events = c(current_event_time, -->
<!--                                          current_obs_time)) -->
<!--         all_Lambda <- c(all_Lambda,Lambda_vec) -->
<!--         n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time) -->
<!--       } -->
<!--       if(length(all_Lambda)>0){ -->
<!--         ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp", -->
<!--                                         rate = 1/mean(all_Lambda))$statistic -->
<!--         Lambda_matrix[i,j][[1]] <- all_Lambda -->
<!--       } -->
<!--     } -->
<!--   } -->
<!-- } -->

<!-- m2_ks <- ks.stat.matrix -->

<!-- # -------------- KS plot (stat) -->
<!-- col.vec <- cRamp(as.vector(ks.stat.matrix)) -->
<!-- ## need to do some sort of transformation between these here -->
<!-- vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix)))) -->
<!-- #order(as.vector(ks.stat.matrix),method = "") -->

<!-- values <- as.vector(ks.stat.matrix) -->
<!-- sorted_vals <- sort(ks.stat.matrix) -->
<!-- #match(values,sorted_vals) -->
<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->

<!-- #### -->
<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
<!--     mgp = c(0, .2, 0)) -->
<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
<!-- for(i in expert_rank_10[[current_cohort]]){ -->
<!--   for(j in expert_rank_10[[current_cohort]]){ -->
<!--     if(ks.stat.matrix[i,j]==0){ -->
<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
<!--            axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
<!--            border = 0, col = 'white') -->
<!--     }else{ -->
<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],  -->
<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->
<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
<!--             ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2) -->
<!--       plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE, -->
<!--            verticals = TRUE, col = "red", lwd = 2) -->
<!--     } -->
<!--   } -->
<!-- } -->
<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->

<!-- col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)), -->
<!--                             length.out = 100), -->
<!--                 col.vec = viridis(100)) -->

<!-- temp <- cLegend(as.vector(ks.stat.matrix)) -->

<!-- image(1, col_obj$x.vec, -->
<!--       matrix(data=col_obj$x.vec,  -->
<!--              ncol=length(col_obj$x.vec),nrow=1), -->
<!--       col=col_obj$col.vec, -->
<!--       xlab="",ylab="",axes=FALSE) -->
<!-- axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1, -->
<!--      cex.axis=2.4) -->

<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
<!--       line=1.8, outer=TRUE, cex=1.8, -->
<!--       at=1/14*c(1:12)-1/22) -->
<!-- mtext(text = expert_rank_10[[current_cohort]], -->
<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
<!--       at =1/12*c(12:1)-1/20, las = 2) -->
<!-- mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE, -->
<!--       cex = 2.2, -->
<!--       at=0.45, font=2) -->

<!-- ``` -->

<!-- ```{r construct ks_diff} -->
<!-- ks_diff <-  (m2_ks - m1_ks)/m1_ks -->
<!-- ks_diff[is.nan(ks_diff)] <- 0 -->
<!-- # -------------- KS plot (stat) -->
<!-- col.vec <- cRamp(as.vector(ks_diff)) -->
<!-- ## need to do some sort of transformation between these here -->
<!-- vir_cols <- viridis::viridis(length((as.vector(ks_diff)))) -->
<!-- #order(as.vector(ks.stat.matrix),method = "") -->

<!-- values <- as.vector(ks_diff) -->
<!-- sorted_vals <- sort(ks_diff) -->
<!-- #match(values,sorted_vals) -->
<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->

<!-- #### -->
<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
<!--     mgp = c(0, .2, 0)) -->
<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
<!-- for(i in expert_rank_10[[current_cohort]]){ -->
<!--   for(j in expert_rank_10[[current_cohort]]){ -->
<!--     if(ks_diff[i,j]==0){ -->
<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
<!--            axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
<!--            border = 0, col = 'white') -->
<!--     }else{ -->
<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->

<!--     } -->
<!--   } -->
<!-- } -->
<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->

<!-- col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)), -->
<!--                             length.out = 100), -->
<!--                 col.vec = viridis(100)) -->

<!-- # temp <- cLegend(as.vector(ks_diff)) -->

<!-- image(1, col_obj$x.vec, -->
<!--       matrix(data=col_obj$x.vec,  -->
<!--              ncol=length(col_obj$x.vec),nrow=1), -->
<!--       col=col_obj$col.vec, -->
<!--       xlab="",ylab="") -->
<!-- # axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1, -->
<!-- #      cex.axis=2.4) -->

<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
<!--       line=1.8, outer=TRUE, cex=1.8, -->
<!--       at=1/14*c(1:12)-1/22) -->
<!-- mtext(text = expert_rank_10[[current_cohort]], -->
<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
<!--       at =1/12*c(12:1)-1/20, las = 2) -->
<!-- mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE, -->
<!--       cex = 2.2, -->
<!--       at=0.45, font=2) -->

<!-- ``` -->

<!-- ```{r construct ks diff normalised by num events} -->
<!-- norm_diff <- (m2_ks - m1_ks)#/m1_ks -->
<!-- norm_diff[is.nan(norm_diff)] <- 0 -->
<!-- count_mat <- matrix(0, nrow = mice_number, ncol = mice_number) -->

<!-- for(i in expert_rank_10[[current_cohort]]) { -->
<!--   for(j in expert_rank_10[[current_cohort]]) { -->
<!--     if( norm_diff[i,j] != 0 ) { -->
<!--       num_events <- unique_pairs_df %>%  -->
<!--       filter(initiator == i & recipient == j) %>% -->
<!--       pull(count) -->
<!--       # diff[i,j] <- diff[i,j] / num_events -->
<!--       count_mat[i,j] <- num_events -->
<!--     } -->
<!--   } -->
<!-- } -->

<!-- tibble(diff_norm = as.vector(norm_diff), -->
<!--        events = as.vector(count_mat)) %>% -->
<!--   filter(events > 0 ) %>% -->
<!--   ggplot(aes(events,diff_norm)) + geom_point() + -->
<!--   ylab("M2-M1") + -->
<!--   theme_minimal() -->

<!-- tibble(diff_norm = as.vector(norm_diff), -->
<!--        events = as.vector(count_mat)) %>% -->
<!--   filter(events > 0) %>% -->
<!--   ggplot(aes(diff_norm)) +  -->
<!--   geom_histogram() + -->
<!--   theme_minimal() -->

<!-- ``` -->
<!-- ```{r repeat for residuals} -->
<!-- m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort], -->
<!--                    "/chp_pr_matrix_",cohort_names[current_cohort], -->
<!--                    ".RDS",sep='')) -->

<!-- m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort], -->
<!--                      "/dchp_pr_matrix_",cohort_names[current_cohort], -->
<!--                      ".RDS",sep='')) -->

<!-- tibble(m1pr = as.vector(m1_pr), -->
<!--        m2pr = as.vector(m2_pr)) %>% -->
<!--   mutate(diff = m2pr - m1pr) %>% -->
<!--   ggplot(aes(diff)) +  -->
<!--   geom_histogram() + -->
<!--   labs(x = "M2 PR - M1 PR") + -->
<!--   theme_minimal() -->

<!-- ``` -->

<!-- ```{r compute mean decrease in ks-score} -->
<!-- summary(as.vector(m2_ks[m2_ks != 0])) -->
<!-- summary(as.vector(m1_ks[m1_ks != 0])) -->

<!-- t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0])) -->

<!-- diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0]) -->

<!-- length(which(diff < 0))/length(diff) -->
<!-- summary(diff) -->
<!-- ``` -->

<!-- This is good because it shows the most active animal, shows that individual -->
<!-- out rate too large for this interaction. Just need to make this more -->
<!-- like the plots in 2b. -->

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=6,fig.width=8}
sim_data_path <- "../output/sims_m3_update/"

@@

```{r prepare data for 4b,cache=TRUE}
plot.s <- 6#7#9
plot.i <- 4
plot.j <- 5

@@

```{r fig4b-recover-latent-states,fig.width=8,fig.height=5}
y.ub <- c(15,15,15)#c(130,72,31)
x_events <- 190#135#150
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#160#200#130
my.long.x <- 205#205#134.5
legend.x <- c(150,150,150)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(12,12,12)#c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## add legend
# changed 34 to 23, 25 to 18, -20 to -10
# legend(10,legend.y[1],c("State 1/0 events","State change point"),
#        col = c(NA,"red"),
#        y.intersp=0.85,x.intersp=-0.1, bty = "n",
#        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
#        lty = c(NA,NA), lwd=c(NA,4))
# points(29,84,pch=1,cex=2,col="blue")
# points(26,84,pch=16,cex=2,col="blue")
legend(legend.x[1],legend.y[1],c("True"),
       col = c("black"),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
legend(legend.x[1]+18,legend.y[1],c("C-HP"),
       col = c(model_colors[1]),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.positive,0),col=positive.col,border=NA)

@@

legend(legend.x[2]-45,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(110,legend.y[2] - 3, pch = 1, cex = 2, col = "blue")
points(113,legend.y[2] - 3, pch = 16, cex = 2, col = "blue")

@@

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
     ylim=c(-2,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

legend(legend.x[3]-45,legend.y[3]+2, c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.6,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

```{r fig5-residual-ks, fig.height=7}
# cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
#                                              "True"))

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=7}
sim_files <- list.files(here("output", "sims_m3_update",
                             "sims_m3_dc_isi_sparse"))

all_sims <- list()
for(i in seq_along(sim_files)) {
 single_fit <- readRDS(here("output", "rank_sims", 
                            "sims_m3_dc_isi_sparse",
                            sim_files[i]))
 all_sims[[i]] <- single_fit
}

@@

```{r fig-rank-slides, fig.height=3,include=slides_plots,eval=slides_plots}

p2_slides <- plot_cor_df %>%
  filter(Method != "Agg-rank") %>%      
  ggplot(aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = viridis::viridis(3)) + 
        #ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Rank correlation")
p2_slides

@@

```{r fig-7-prMatrix-Cohort5, fig.width=7, fig.height=7}
current_cohort <- 5

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )
mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
# current_cohort <- 5

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'pdf', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

@@

```{r fig-3b-rank-comparison, include=FALSE,eval=FALSE}
# current_cohort <- 5

@@

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=3.5,fig.width=8}
sim_data_path <- "../output/sims_m3_update/"

@@

```{r prepare data for 4b,cache=TRUE}
plot.s <- 7#7 is pretty good
plot.i <- 4
plot.j <- 5

@@

```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4}
y.ub <- c(35,35,35)#c(130,72,31)
x_events <- 190#135#150
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#160#200#130
my.long.x <- 205#205#134.5
legend.x <- c(60,60,60)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(23,23,23)#c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue')
positive.col <- add.alpha('tomato')
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## add legend
# changed 34 to 23, 25 to 18, -20 to -10
# legend(10,legend.y[1],c("State 1/0 events","State change point"),
#        col = c(NA,"red"),
#        y.intersp=0.85,x.intersp=-0.1, bty = "n",
#        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
#        lty = c(NA,NA), lwd=c(NA,4))
# points(29,84,pch=1,cex=2,col="blue")
# points(26,84,pch=16,cex=2,col="blue")
legend(legend.x[1],legend.y[1],c("True"),
       col = c("black"),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
legend(legend.x[1]+22,legend.y[1],c("C-HP"),
       col = c(model_colors[1]),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.positive,0),col=positive.col,border=NA)

@@

legend(legend.x[2]-50,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.5, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,2))
points(legend.x[2]-46,legend.y[2] - 4.5, pch = 1, cex = 2, col = "blue")
points(legend.x[2]-44,legend.y[2] - 4.5, pch = 16, cex = 2, col = "blue")

@@

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
     ylim=c(-4,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

legend(legend.x[3]-50,legend.y[3]+2, c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.75,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

```{r fig5a-residual-ks, fig.height=7}
# cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
#                                              "True"))

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=7}
sim_files <- list.files(here("output", "sims_m3_update"), 
                        pattern = "rank_sim")

all_sims <- list()
for(i in seq_along(sim_files)) {
 single_fit <- readRDS(here("output", "sims_m3_update",
                            sim_files[i]))
 all_sims[[i]] <- single_fit
}

@@

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 3
## 2 and 8 maybe look better
## 3 probably looks the best

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )
# mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@
